Analysis of the properties of probabilistic models in learning problems with an expert\thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2020-12-30 paper/Bazarova2020Springer/article.tex
fixed

\section{Introduction}
\label{intro}
Interpretable model building in machine learning~\cite{Ribeiro2016} is one of the key challenges.
Modern solutions of the image classification problem based on deep learning networks ResNet, VGG, Intercept~\cite{Kaiming2015} are poorly interpreted models.
The papers~\cite{Han2020} \cite{Akhtar2018} show that deep learning networks are sensitive even to small noise in the data, which is due to their uninterpretability.

@@

This paper solves the problem of approximating second-order curves on a contour image. Second-order curves are selected for analysis, since they are easily described by linear models. In this case, these figures need to be restored in such applied problems as the problem of recognizing the iris of the eye~\cite{Matveev2010} \cite{Matveev2014} \cite{Bowyer2010}, the problem of describing the particle track in the hadron collider~\cite{Dalila2018}. Expert information about a second-order curve allows you to map points on a plane into a new feature description, where each curve is approximated by one linear model. A model that approximates one curve is called a \textit {local model}. To approximate the entire contour image, it is required to approximate several second-order curves using several local models. In this paper, the following restrictions on images are introduced:
\begin{enumerate}
	\item the image consists only of second-order curves;
	\item the image is approximated by a small number of second-order curves;
	\item the number and type of curves in the image is known.
\end{enumerate}

@@

When approximating several curves on one contour image, a multi-model is built. An example of multi-models is a random forest~\cite{Ishwaran2012}, tree boosting~\cite{Tianqi2016}, a mixture of experts~\cite{Yuksel2012}. In this paper, a mixture of experts is considered as a multi-model. Expert mixture is a multi-model that linearly weights local models that approximate a portion of the sample. The values of the weighting coefficients depend on the object for which the prediction is made. To solve the problem of a mixture of experts, a variational EM-algorithm~\cite{Dempster1977} \cite{bishop2006} \cite{Peng1996} is used. The mixture of experts has many uses in a number of applications. In the paper~\cite{Estabrooks2001}, the text classification problem is solved. In the paper~\cite{Cheung1995} \cite{Weigend2000} \cite{Cao2003} \cite{Mossavat2010} \cite{Sminchisescu2007} \cite{Tuerk2001} \cite{Yumlu2003}, a mixture of experts is used to predict time series for speech recognition, daily human activity, and prediction of the value of securities. In the paper~\cite{Ebrahimpour2009}, a mixture of experts was considered to solve the problem of recognizing handwritten numbers in images.

@@

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{Ribeiro2016}
Ribeiro M, Singh S, Guestrin C (2016) Why Should I Trust You?": Explaining the Predictions of Any Classifier. KDD ’16 Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining 1135--1144

@@

\bibitem{Ebrahimpour2009}
Estabrooks A, Japkowicz N (2009) Recognition of Persian handwritten digits using characterization loci and mixture of experts. J. Digital Content Technol. Appl. 42--46

\bibitem{Estabrooks2001}
Ebrahimpour R, M. Moradian R, Esmkhani A, Jafarlou F (2009) A mixture-of-experts framework for text classification. In Proc. Workshop Comput. Natural Lang. Learn., Assoc. Comput. Linguist. 1--8

@@

@@

\bibitem{Akhtar2018}
Akhtar N, Mian A (2018) Threat of Adversarial Attacks on Deep Learning in Computer Vision: A Survey. IEEE Access 6:14410--14430

>>>>

\section{Introduction}
\label{intro}
Interpretable model building in machine learning~(Ribeiro et al. 2016) is one of the key challenges.
Modern solutions of the image classification problem based on deep learning networks ResNet, VGG, Intercept~(Kaiming et al. 2016) are poorly interpreted models.
The papers~(Han et al. 2020; Akhtar et al. 2018) show that deep learning networks are sensitive even to small noise in the data, which is due to their uninterpretability.

@@

This paper solves the problem of approximating second-order curves on a contour image. Second-order curves are selected for analysis, since they are easily described by linear models. In this case, these figures need to be restored in such applied problems as the problem of recognizing the iris of the eye~(Matveev 2010; Matveev et al. 2014; Bowyer et al. 2010), the problem of describing the particle track in the hadron collider~(Salamani et al. 2018). Expert information about a second-order curve allows you to map points on a plane into a new feature description, where each curve is approximated by one linear model. A model that approximates one curve is called a \textit {local model}. To approximate the entire contour image, it is required to approximate several second-order curves using several local models. In this paper, the following restrictions on images are introduced: a) the image consists only of second-order curves; b) the image is approximated by a small number of second-order curves; c) the number and type of curves in the image is known.

@@

When approximating several curves on one contour image, a multi-model is built. An example of multi-models is a random forest~(Chen et al. 2012), tree boosting~(Chen et al. 2016), a mixture of experts~(Yuksel et al. 2012). In this paper, a mixture of experts is considered as a multi-model. Expert mixture is a multi-model that linearly weights local models that approximate a portion of the sample. The values of the weighting coefficients depend on the object for which the prediction is made. To solve the problem of a mixture of experts, a variational EM-algorithm~(Dempster et al. 1997; Bishop 2010; Peng et al. 1996) is used. The mixture of experts has many uses in a number of applications. In the paper~(Estabrooks et al. 2001), the text classification problem is solved. In the papers~(Cheung et al. 1995; Weigend et al. 2000; Cao 2003; Mossavat et al. 2010; Sminchisescu C et al. 2007; Tuerk 2001; Yumlu et al. 2003), a mixture of experts is used to predict time series for speech recognition, daily human activity, and prediction of the value of securities. In the paper~(Ebrahimpour et al. 2009), a mixture of experts was considered to solve the problem of recognizing handwritten numbers in images.

@@

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{Akhtar2018}
Akhtar N, Mian A (2018) Threat of Adversarial Attacks on Deep Learning in Computer Vision: A Survey. IEEE Access 6:14410--14430

@@

\bibitem{Estabrooks2001}
Estabrooks A, Japkowicz N (2001) A mixture-of-experts framework for text classification. In Proc. Workshop Comput. Natural Lang. Learn., Assoc. Comput. Linguist. 1--8

\bibitem{Ebrahimpour2009}
Ebrahimpour R, Moradian R, Esmkhani A, Jafarlou F (2009) Recognition of Persian handwritten digits using characterization loci and mixture of experts. J. Digital Content Technol. Appl. 42--46

@@

\bibitem{Ribeiro2016}
Ribeiro M, Singh S, Guestrin C (2016) Why Should I Trust You?": Explaining the Predictions of Any Classifier. KDD ’16 Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining 1135--1144

@@
